Title

### 2014-11-14 manuscript.tex
Numerical integration section draft

Thus, the roots must be scaled to the integration limits $[a, b]$ by
\begin{equation}
    x^{scaled}_i = \frac{b - a}{2} x_i + \frac{b + a}{2}.
\end{equation}

The weights of the GLQ are given by \citep{Hildebrand1987},
\begin{equation}
    W_i = \frac{2}{(1 - x_i^2)(P^\prime_N(x_i))^2},
\end{equation}

The values of the $P_N(x)$ and its first derivative $P^\prime_N(x)$ can be
calculated with recursive relations (PUT FORMULA HERE?).

@@

The latest version can be downloaded from the official
website\footnote{http://www.leouieda.com/tesseroids}.

@@

The \texttt{src} folder of the distribution archive
contains the \texttt{.c} files that build the command-line programs.

@@

The first step in the numerical integration with the GLQ is to compute the
locations of the point masses (i.e., the discretization points).

@@

We use the

>>>>

Thus, the roots must be scaled to the integration limits $[a, b]$ by
\begin{equation}
    x^{scaled}_i = \frac{b - a}{2} x_i + \frac{b + a}{2}.
    \label{eq:glq_scaling}
\end{equation}

The weights of the GLQ are given by \citep{Hildebrand1987},
\begin{equation}
    W_i = \frac{2}{(1 - x_i^2)(P^\prime_N(x_i))^2},
    \label{eq:glq_weights}
\end{equation}

The values of the $P_N(x)$ and its first derivative $P^\prime_N(x)$ can be
calculated with recursive relations.

@@

The official website\footnote{http://www.leouieda.com/tesseroids}
hosts the software documentation and
archives of the latest binary executables and source code.

@@

The \texttt{src} folder of the distribution archive
contains the C files that build the command-line programs
(e.g., \texttt{tessgz.c}).

@@

The source file \texttt{src/lib/glq.c} contains the code necessary to perform a
Gauss-Legendre Quadrature integration.

The first step in the GLQ is to compute the
locations of the point masses (i.e., the discretization points).

@@

Precomputed values for these roots are available low order polynomials,
usually up to order 5.

For flexibility, we use the multiple root-finder algorithm of
\citet{Barrera-Figueroa2006} to compute the roots for polynomials of any order.

The additional computational load is minimal since the root-finder algorithm
must be run only once per program execution.

The root-finder algorithm is implemented in functions \texttt{glq\_nodes} and
\texttt{glq\_next\_root}.

The computed roots will be in the range $[-1, 1]$
and must be scaled to the integration limits (the limits of the tesseroid)
using function \texttt{glq\_set\_limits} (see equation~\ref{eq:glq_scaling}).

The GLQ weights are computed using equation~\ref{eq:glq_weights} by function
\texttt{glq\_weights}.

Both the computed roots and weights are stored in a data structure (a C
\texttt{struct}) called \texttt{GLQ}.

Function \texttt{glq\_new} allocates the memory necessary,
calculates the roots and weights,
and returns the complete \texttt{GLQ} structure.

The numerical integration is performed by the functions in module
\texttt{src/lib/grav\_tess.c}.

The functions \texttt{tess\_pot}, \texttt{tess\_gx}, \texttt{tess\_gy},
and so on, compute the gravitational fields of a single tesseroid on a single
computation point using the GLQ.

These functions require three \texttt{GLQ} structures with roots scaled to the
integration limits $[\lambda_1, \lambda_2], [\phi_1, \phi_2], [r_1, r_2]$.

The integration consists of three \texttt{for} loops: one for longitude, one
for latitude, and one for radius.

The evaluation of the trigonometric functions in
equations~\ref{eq:tesspot}-\ref{eq:tesstensor} inside the inner loops
are the biggest bottlenecks for the numerical integration.

Better performance is achieved by moving some trigonometric function
evaluations to the outer loops
and precomputing the sine and cossine of latitudes.
